Writing a reproducible paper with R Markdown and Pagedown^[Corresponding adress: mail@paulcbauer.eu, camille.landesvatter@mzes.uni-mannheim.de]

### 2021-06-23 paper.Rmd
Small text edits.
modified tables.

I would recommend to use the command below and simply add it to the appendix as I did here in Appendix \@ref(sec:rsessioninfo). This will make sure you always provide the package versions that you used in the last compilation of your paper. For more advanced tools see [packrat](https://rstudio.github.io/packrat/).

@@

```{r table-4, echo=TRUE}
# Create categorical variables
mtcars$vs_cat <- as.logical(mtcars$vs)
mtcars$cyl_cat <- as.factor(mtcars$cyl)
datasummary_skim(mtcars, 
                 type="categorical", 
                 title = "Summary: Categorical variables")
```

@@

modelsummary(models, title = 'A regression table.')
```

>>>>

I would recommend to use the command below and simply add it to the appendix as I did here in Appendix \@ref(sec:rsessioninfo). This will make sure you always inform the reader about the package versions your relied on in your paper. For more advanced tools see [packrat](https://rstudio.github.io/packrat/).

@@

```{r table-4, echo=TRUE}
# Create categorical variables
mtcars$vs_cat <- as.logical(mtcars$vs)
mtcars$cyl_cat <- as.factor(mtcars$cyl)

library(flextable)
tab_cat <- datasummary_skim(mtcars, 
                            type="categorical", 
                            title = "Summary: Categorical variables",
                            output = 'flextable')

# additionally we want to change the font, fontsize and spacing
library("gdtools")

library(dplyr)
tab_cat <- tab_cat %>%
  font(fontname="Times New Roman", part="header") %>%
  font(fontname="Times New Roman", j=1:4) %>% 
  fontsize(size=12, part="header") %>%
  fontsize(size=10, j=1:4) %>% 
  line_spacing(space = 0.3, part = "all")

tab_cat
```

@@

tab_reg <-modelsummary(models, title = 'A regression table.', output = 'flextable')

# additionally we want to change the font, font size and spacing
library("gdtools")

tab_reg <- tab_reg %>%
  font(fontname="Times New Roman", part="header") %>%
  font(fontname="Times New Roman", j=1:4) %>% 
  fontsize(size=10, part="header") %>%
  fontsize(size=10, j=1:4) %>% 
  line_spacing(space = 0.3, part = "all")

tab_reg
